Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\section{Results and Discussion}
Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets in which we mark as bold for the best ROC-AUC on each dataset. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively. And the big gap is in the Condmat dataset with 7.4$\%$.

\begin{table}
\caption{The ROC-AUC performance on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores. }
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|}

>>>>

\section{Results and Discussion}
In table \ref{result_table} we report the performance of link prediction methods measured as the AUC-ROC value on 6 datasets. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively. And the big gap is in the Condmat dataset with 7.4$\%$.

\begin{table}
\caption{AUC-ROC performance on 6 datasets. Legend: AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores, JNSL: joint neighborhood subgraph link (our method). In bold the highest score.}
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|}
